---
name: Christopher
surname: Wenz
address: "456 Long Plain Road · Leverett, MA 01054"
phone: 860-977-1674
email: "cawenz@gmail.com"
profilepic: "./img/bwwenz.png"
#github: cawenz
linkedin: chris-a-wenz
researchgate: chris_wenz
headcolor: 5b9279
docname: Short CV
output: vitae::awesomecv
#aboutme: "An experienced educator committed to creating accessible and responsive educational environments that work for ***all*** students."
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(vitae)
library(tibble)
library(magrittr)
library(here)
library(readr)
source(file = here("r","data2.r"))
```
# Education
```{r ed alt}
educationDETAIL %>%
  detailed_entries(
    with = school, 
    what = degree, 
    when = Year,
    where = city,
  )
```

# Experience
```{r Experience}
experience %>%
  detailed_entries(
    with = employer,
    what = title,
    why = why,
    when = glue::glue("{startYear} --- {endYear}",.na = ""),
    where = where,
  )
```

# Teaching
## $\text{\underline{Graduate Courses}}$
Note: ** indicates online courses
```{r grad_teach}
tribble(
  ~Year, ~Name, ~Duty, ~School,
  '2019 --- Present', "Reframing autism**", "Designer and Instructor", "Landmark College",
  '2018 --- Present',"Learning Differences and Neurodiversity", "Co-Instructor", "Landmark College",
  '2015 --- 2018', "Reading in the Content Areas", "Designer and Instructor", "UConn",
  '2015 --- 2019', "Instruction for Students with Special Needs in the Mainstream","Instructor", "UConn"
) %>% 
  detailed_entries(
    where = School,
    with = Name, 
    what = Duty,
    when = Year
  )
```

## $\text{\underline{Undergraduate Courses}}$
```{r UCONNunder}
tribble(
  ~Year, ~Name, ~Duty, ~School,
  '2018 --- 2020', "Internship Experience", "Design and supervise internships in neuro-cognitive research", "Landmark College",
  '2016 --- 2018', "Teaching Reading and Writing in the Content Areas", "Instructor", "UConn",
  '2015', "History of Mathematics (Writing Intensive)", "Teaching Assistant and Co-Designer","UConn",
  '2013 --- 2015', "Social Thinking: Where’s the syllabus for that?", "Co-Designer and Instructor", "UConn"
) %>% 
detailed_entries(
    where = School,
    with = Name, 
    what = Duty,
    when = Year
  )
```

# Publications
## $\text{\underline{Articles in refereed journals}}$
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
Gabriel, R., \textbf{Wenz, C.} (2017). Three Directions for Disciplinary Literacy. \emph{Educational Leadership}, 74(5), Online Supplement to the February 2017 issue: https://lcirt.link/gabrielandwenz2017.

Gabriel, R., \textbf{Wenz, C.}, \& Dostal, H. (2016). Disciplinary Text-Dependent Questions: Questioning for Learning in the Disciplines. The Challenge of Literacy in the Disciplines. \emph{The Clearing House: A Journal of Educational Strategies, Issues and Ideas,} 89(6), 202–207. https://doi.org/10.1080/00098655.2016.1209154
```
## $\text{\underline{Book Chapters}}$
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\textbf{Wenz, C.}, Kowitt, J. \& Friedlander, L. (2017). A Museum Based Program to Support Adolescents and Adults with ASD: Results of a Pilot Study and Suggestions for Implementation. In, \emph{Examining the Intersection of Arts and Special Education, Volume 3.} Kennedy Center for Performing Arts, Washington, DC.
%\pagebreak
```

# Selected Presentations
## $\text{\underline{Invited Professional Development Workshops}}$
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\textbf{Universal Design and Backwards Design: tools for inclusive and engaging post-secondary instruction.} Full-day workshop for the faculty of Cambridge College, February 18, 2020, Boston, MA. 

\textbf{Executive Function and Student Learning: supporting adolescent development across contexts.} Half-day workshop for the Faculty and Staff of Wilbraham \& Monson Academy, Jan 19, 2020, Wilbraham, MA. 

\textbf{Supporting Social Emotional Learning}. 3-day Workshop at Landmark College's Summer Institute for Educators, June 24-26, 2019, Putney, VT.  

\textbf{Assessment as Instruction: promoting college success for neurodivergent learners.} Full-day workshop for City University of New York's Early College Initiative, May 19, 2019, New York, NY. 

\textbf{Disabilities, Difficulties and Differences: ESOL instruction for diverse learners}. Full-day presentation for the Massachusetts Adult Education Professional Development System, March 29, 2019, Worcester, MA. 

```

## $\text{\underline{National and Regional Conferences}}$
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\textbf{Wenz, C.} \& Warrnader, K. (2018). \emph{The College Writing Motivation Scale: a tool for measuring motivation in Writing Center contexts.} Paper presented at the Northeast Writing Center Association Conference, Worcester, MA.

\textbf{Wenz, C.} (2017). \emph{Disciplinary literacy and journalism: literacy instruction in a post-truth world.} Paper presented at the Literacy Research Association Annual Conference, Tampa, FL.

Kowitt, J., \textbf{Wenz, C.} \& Friedlander, L. (2017). \emph{Enhancing Observational Skills: inclusive museum programming for visitors with Autism.} Paper presented at the Tenth International Conference on the Inclusive Museum, Manchester, UK.

Gabriel, R., \textbf{Wenz, C.} (2015). \emph{The Opportunities to Develop Literacy Scale.} Paper presented at the Literacy Research Association Annual Conference, Carlsbad, CA.

\textbf{Wenz, C.}, \& Gabriel, R. (2015). \emph{An integrative review and pilot survey of disciplinary literacy instruction in secondary settings.} Poster presented at the Annual Meeting of the American Educational Research Association, Chicago, IL
```

# Awards
```{=latex}
\begin{cvhonors}
  \cvhonor
    {Jeanne S. Chall Graduate Fellowship}
    {,  International Literacy Association}
    {Newark, DE}
    {2017}
  \cvhonor
    {Wirth-Santoro Award}
    {,  Connecticut Association for Reading Research}
    {Simsbury, CT}
    {2016}
  \cvhonor
    {Graduate Student Scholarship}
    {,  American Reading Forum}
    {Miami, FL}
    {2016}
  \cvhonor
    {Assessment Award}
    {,  Neag School of Education}
    {Storrs, CT}
    {2013}
    
\end{cvhonors}
```

# Professional Affiliations
```{=latex}
\begin{minipage}[t]{.5\linewidth}
  \begin{cvitems}
    \item College Reading and Learning Association
    \item Council for Exceptional Children
    \item International Literacy Association
  \end{cvitems}
\end{minipage}
\begin{minipage}[t]{.5\linewidth}
  \begin{cvitems}
    \item Literacy Research Association
    \item American Educational Research Association
    \item International Mind, Brain and Education Society
  \end{cvitems}
\end{minipage}
```