---
name: Chris
surname: Wenz
address: "52 River Road Sunderland, MA 01375"
phone: 860-977-1674
email: "cawenz@gmail.com"
profilepic: "./img/bwwenz.png"
github: cawenz
linkedin: chris-a-wenz
researchgate: chris_wenz
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 990000
docname: Cover Letter
output: vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(vitae)
library(tibble)
library(magrittr)
library(here)
library(readr)
source(file = here("r","data2.r"))
```
# Education
**University of Connecticut** (UCONN)--- Storrs, CT
```{r graduate}
graduate %>%
  brief_entries(
    with = year,
    what = school,
    when = degree,
  )
```
**Hampshire College** --- Amherst, MA
```{r undergraduate}
undergraduate %>%
  brief_entries(
    with = year,
    what = school,
    when = degree,
  )
```

# Experience
```{r Experience}
experience %>%
  detailed_entries(
    with = employer,
    what = title,
    why = why,
    when = glue::glue("{startYear} --- {endYear}",.na = ""),
    where = where,
  )
```
# Teaching
## Graduate Courses
```{r grad_teach}
tribble(
  ~Year, ~Name, ~Duty, ~School,
  '2019 --- Present', "Reframing autism", "Designer and Instructor", "Landmark College",
  '2018 --- Present',"Learning Differences and Neurodiversity", "Co-Instructor", "Landmark College",
  '2015 --- 2018', "Reading in the Content Areas", "Designer and Instructor", "UCONN",
  '2015 --- 2019', "Instruction for Students with Special Needs in the Mainstream","Instructor", "UConn"
) %>% 
  detailed_entries(
    where = School,
    with = Name, 
    what = Duty,
    when = Year
  )
```
## Undergraduate Courses
```{r UCONNunder}
tribble(
  ~Year, ~Name, ~Duty, ~School,
  '2018 --- 2020', "Internship Experience", "Design and supervise internships in neuro-cognitive research, graphic design, and software development", "Landmark College",
  '2017 --- 2018', "Teaching Reading in the Middle and High School", "Instructor", "UCONN",
  '2016 --- 2018', "Teaching Reading and Writing in the Content Areas", "Instructor", "UCONN",
  '2015', "History of Mathematics (Writing Intensive)", "Teaching Assistant and Co-Designer","UCONN",
  '2013 --- 2015', "Social Thinking: Where’s the syllabus for that?", "Co-Designer and Instructor", "UCONN"
) %>% 
detailed_entries(
    where = School,
    with = Name, 
    what = Duty,
    when = Year
  )
```

# Publications
## $\text{\underline{Articles in refereed journals}}$
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
Gabriel, R., \textbf{Wenz, C.} (2017). Three Directions for Disciplinary Literacy. \emph{Educational Leadership}, 74(5), Online Supplement to the February 2017 issue: https://lcirt.link/gabrielandwenz2017.

Gabriel, R., \textbf{Wenz, C.}, \& Dostal, H. (2016). Disciplinary Text-Dependent Questions: Questioning for Learning in the Disciplines. The Challenge of Literacy in the Disciplines. \emph{The Clearing House: A Journal of Educational Strategies, Issues and Ideas,} 89(6), 202–207. https://doi.org/10.1080/00098655.2016.1209154
```
## Book Chapters
```{=latex}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\textbf{Wenz, C.}, Kowitt, J. \& Friedlander, L. (2017). A Museum Based Program to Support Adolescents and Adults with ASD: Results of a Pilot Study and Suggestions for Implementation. In, \emph{Examining the Intersection of Arts and Special Education, Volume 3.} Kennedy Center for Performing Arts, Washington, DC.
%\pagebreak
```
# Selected Presentations
## Professional Development Workshops

## At Local and National Conferences





# Awards
```{r HONORS}

honors %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Projects

```{r PROJECTS}

projects %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Works

```{r WORKS}

works %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Certifications

```{r CERTIFICATIONS}

certifications %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```


